% ============================================================
% Compiler-as-Reward: Operating-Regime Conditions for RL on Coding Agents
% ICML 2026 Workshop: Deep Learning for Code: Human-Centered Coding Agents
% ============================================================
\documentclass[10pt]{article}

% Layout — 4-page workshop paper
\usepackage[margin=1in,top=1.1in,bottom=1.1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}

% Tighter section spacing for 4-page limit
\titlespacing*{\section}{0pt}{8pt plus 2pt minus 2pt}{4pt plus 1pt}
\titlespacing*{\subsection}{0pt}{6pt plus 1pt}{3pt plus 1pt}

\setlength{\parskip}{3pt}
\setlength{\parindent}{0pt}

\definecolor{darkblue}{RGB}{0,60,120}
\definecolor{darkred}{RGB}{160,0,0}
\definecolor{darkgreen}{RGB}{0,110,0}

\hypersetup{
  colorlinks=true,
  linkcolor=darkblue,
  citecolor=darkblue,
  urlcolor=darkblue
}

\captionsetup{font=small,labelfont=bf,skip=4pt}

% ============================================================
\title{\textbf{Compiler-as-Reward: Operating-Regime Conditions for\\
Agentic RL on Verifiable Coding Tasks}}

\author{
  Junhao Fu \\
  \small{\texttt{junhao.fu@sorcara.com}}
}

\date{}

% ============================================================
\begin{document}
\maketitle
\vspace{-10pt}

% ============================================================
\begin{abstract}
A common assumption in multi-turn coding-agent RL is that sparse pass/fail rewards
are the bottleneck and must be densified through hand-designed process rewards.
We test this on a Shopify Horizon theme-generation task—an \emph{agentic RL}
setting~\cite{cursor2025composer2,kimi2025k2} with tool use, multi-turn
interaction, and a deterministic compiler-API reward—and find the opposite:
\textbf{the bottleneck is the operating regime, not the reward shape}. A 4B
base model has a 7.8\% compile-pass rate from free-form prompting; a single
in-context schema example lifts the base to 73.4\% \emph{before any RL
training}. In this regime, plain GiGPO~\cite{zeng2025gigpo} with binary outcome
reward improves a held-out OOD task set by +9pp (40.9\% $\to$ 50.0\%); on
in-distribution validation it reaches 78\%. We then test three process-reward
variants. Compiler-OPD (per-step credit on validate calls) is analyzed but not
run, owing to a Goodhart-style failure mode that requires a hand-tuned cap.
Best-Trajectory Distillation~\cite{lambert2025tulu3} (SFT-on-winners mixed
with the policy-gradient loss) is run end-to-end and \emph{underperforms the
binary baseline by 22.7pp on OOD}, recovering training distribution but
discarding generalization. Cursor-style auxiliary product
penalties~\cite{cursor2025composer2} (penalize empty sections / unused tool
calls / repeated submits) destabilize the run on our small-batch (64
episodes/step) setting and fail to exceed the binary baseline on in-loop
validation. We argue that for verifiable coding tasks at compute-constrained
scale, energy is better spent ensuring base success rate is non-negligible
(via priming or warm-starting) than on hand-designed step rewards. Concurrent
work~\cite{ramp2026fastask,hu2025orz} reaches the same conclusion on
spreadsheet retrieval and on pure-RL math reasoning, respectively.
\end{abstract}

% ============================================================
\section{Introduction}
\label{sec:intro}

Reinforcement learning from execution feedback (RLEF)~\cite{le2022coderl,shao2024grpo}
is a standard recipe for code generation: generate, execute, collect binary
pass/fail, optimize. Multi-turn coding agents that use tools (read, edit,
validate) inherit a long-horizon credit assignment problem on top of this:
in a 6-turn episode every failed trajectory looks the same regardless of how
far the agent got, and group-relative algorithms like GRPO/GiGPO produce zero
gradient when an entire rollout group fails. The proposed remedies fall into
two families. The first hand-designs per-step rewards that fire on
intermediate ``good'' actions, e.g.\ a tool-use credit
(\textsc{Compiler-OPD}, \cite{wang2024mathshepherd}-style PRMs). The second
imitates winning trajectories via an auxiliary SFT loss (Best-Trajectory or
``on-policy SFT''~\cite{lambert2025tulu3}). Both pay a coupling tax: any signal
not perfectly aligned with the verifier creates Goodhart pressure, and the
literature documents this in PRM-style training as ``reward hacking that
collapses validation accuracy''~\cite{lambert2025tulu3}.

This paper reports a small empirical study that arrives at a more boring
conclusion. On a Shopify Horizon theme-editing task with a deterministic
compiler-API reward, the regime that requires reward shaping is the
\emph{symptom of a poorly chosen base policy}. With a single in-context
example showing valid template structure, the 4B base model's compile-pass
rate jumps from 7.8\% to 73.4\%, putting the policy in a regime where
group-relative advantage has nonzero variance and ordinary GiGPO with
binary outcome reward already converges. Process-reward variants designed
to be ``cleaner'' than reward shaping---specifically a Best-Trajectory SFT
auxiliary loss---fail to improve on this baseline and damage out-of-distribution
generalization.

\textbf{Contributions.}
(1) An empirical decomposition of where RL gains come from on this
\emph{agentic} task: operating-regime priming dominates RL training
(+65.6pp vs +6.4pp).
(2) Two clean negative ablations on this regime:
(a) Best-Trajectory Distillation auxiliary loss \emph{hurts} OOD
generalization (\(-22.7\)pp on a held-out modify/add/create task set);
(b) Cursor Composer 2-style product
penalties~\cite{cursor2025composer2}---ported as the closest agentic-RL
analogue---fail to exceed the binary baseline on in-loop validation
and exhibit volatile training dynamics in our 64-episode-per-step
regime.
(3) An open Sitemuse-API-grounded benchmark with deterministic reward,
suitable for further verifiable-RL studies.

% ============================================================
\section{Problem Setup}
\label{sec:setup}

\textbf{Task.} Each episode presents a natural-language design request and a
template type (e.g.\ \texttt{page.faq}). The agent must produce a JSON template
that compiles cleanly under Shopify's live validator. Training has 423 prompts;
held-out splits are val (50, in-distribution) and \texttt{eval\_fixed} (22 OOD
modify/add/create tasks from prior baseline work).

\textbf{Action grammar (5 verbs).}
\texttt{list\_sections[]}, \texttt{describe\_section[name]},
\texttt{describe\_block[name]} are read-only theme inspection;
\texttt{fix[json]} compiles a draft (returns errors as next observation; passes
auto-terminate); \texttt{submit[json]} commits the final answer
(always terminal). \texttt{max\_steps} = 6.

\textbf{Reward oracle.} The Sitemuse \texttt{themeFilesUpsert} GraphQL endpoint
takes the candidate template and returns \texttt{userErrors}. Compile-pass
yields $r_T = +1$, fail yields $r_T = 0$. An invalid action (no parseable
\texttt{<action>}) gets $r_t = -0.1$.

\textbf{Base algorithm.} GiGPO~\cite{zeng2025gigpo} on Qwen3-4B-Instruct via
verl-agent. LoRA rank 32, learning rate $3{\times}10^{-6}$, group size 8,
$\mathrm{train\_batch}=8$ (so 64 episodes per gradient step). All variants
share this backbone.

% ============================================================
\section{Method: What Helps, What Does Not}
\label{sec:method}

\subsection{Operating-Regime Priming (the single biggest lever)}

The base prompt asks for a Shopify template in JSON. Without further
guidance, Qwen3-4B generates JSON whose top-level shape does not match
Shopify's conventions: \texttt{sections} as an array instead of an object
keyed by user-chosen IDs; sections without a \texttt{type} field; etc.
Compile-pass: \textbf{7.8\%}.

We add a single fully worked example to the system prompt:

\begin{verbatim}
{ "sections": { "my_hero": { "type": "hero",
                              "settings": {}, "blocks": {} }},
  "order": ["my_hero"] }
\end{verbatim}
plus 5 short structural notes (\texttt{sections} is an object, instance ID is
free, \texttt{type} is required, etc.). The base model's compile-pass rate
on \texttt{val.jsonl} jumps to \textbf{73.4\%}: a $+65.6$pp lift before any
RL takes place. This single intervention dominates every RL effect we
observe and changes the regime in which RL operates.

\subsection{GiGPO + Binary Outcome (variant v1)}

In the primed regime, $\mathrm{P}(\text{group fully fails}) = (1-p)^{|G|}$
with $p \approx 0.73$ and $|G|=8$ is $\approx 1\!\times\!10^{-4}$, so almost
every group has nonzero advantage variance. Standard GiGPO with $r_T \in \{0, 1\}$
(plus the $-0.1$ invalid-action penalty) converges without further
intervention. This is variant \textbf{v1}.

\subsection{What Did Not Work}

\textbf{Compiler-OPD (analyzed; not run).}
We considered a per-step reward $r_t = +0.1$ for the first $K=2$
\texttt{fix} calls (Math-Shepherd-style~\cite{wang2024mathshepherd}
process credit, capped to discourage spamming). The cap is a
hand-tuned magic number with no first-principles justification: $K=1$
is too tight, $K=\infty$ rewards redundant validation, $K=2$ is
chosen heuristically. We did not run it: the failure mode it produces
(reward rising while val collapses; ``M1 hack'' in earlier
notes~\cite{wang2024mathshepherd}) is well documented and the
operating-regime fix from \S3.1 already removes the sparseness it was
designed to patch.

\textbf{Best-Trajectory Distillation (variant v2-distill, run end-to-end).}
A more principled alternative is to add an auxiliary SFT loss on tokens
of \emph{winning} trajectories~\cite{lambert2025tulu3}:
\[
\mathcal{L}_{\mathrm{total}} = \mathcal{L}_{\mathrm{GiGPO}}
+ \alpha \cdot \mathcal{L}_{\mathrm{SFT}}^{\,R \ge 0.5},
\quad \alpha = 0.1.
\]
The mask uses the same compile-pass signal that defines the RL reward,
so it carries no hand-designed step shape. We ran this for 73 steps
(LoRA saved at steps 20, 40, 60). In-loop validation peaked at step 60
(82.8\% on the 32-prompt fixed prefix), but a clean re-evaluation on
$n=50$ val + $n=50$ test + $n=22$ eval\_fixed told a different story
(Table~\ref{tab:main}). The auxiliary SFT loss memorized
training-distribution patterns on the small 423-prompt training set,
losing OOD generalization. Final \texttt{eval\_fixed} dropped from
$50.0\%$ (v1) to $27.3\%$ (v2-distill), $-22.7$pp.

\textbf{Cursor-style product penalties (variant v3-shaped, run end-to-end).}
Composer 2~\cite{cursor2025composer2} introduces ``product-specific
penalties for poor tool calls---e.g.\ creating to-do list items and
then leaving them unfinished''---as an auxiliary reward beyond
correctness. We port this idea to our setting as four
content-aware penalties applied at compile-pass terminals only:
$-0.05$ per declared section with empty \texttt{settings} \emph{and}
\texttt{blocks} (the empty-shell hack the agent learns under
content-blind compile reward), $-0.03$ per \texttt{describe\_X}
without \texttt{X} appearing in the submitted JSON, $+0.04$ per
\texttt{describe\_X} used, $-0.10$ for a \texttt{submit} whose JSON
equals the previous \texttt{fix} (theatrical iteration).
The reward range expands from $\{0, 1.0\}$ to approximately
$[0.45, 1.15]$ on compile-pass outputs, intended to give GRPO
within-group advantage variance even on the bimodal batches we
observe in v1. In-loop validation (32-prompt fixed prefix) over the
first 40 training steps gives $\{73.4, 71.9, 57.8, 71.9, 71.9\}$ at
steps $\{0, 10, 20, 30, 40\}$: stagnant at the base rate, with a deep
dip at step 20. By contrast, the simultaneous \emph{pure-binary} run
(``v1-replica'') reached 81.2\% at step 30 in-loop. The shaped reward
appears to disrupt GRPO's group normalization at our 64-episode batch
size---each shaped reward value is a small perturbation, but when the
group's underlying outcome distribution is already bimodal (\S
\ref{sec:trajectories}, $\mathrm{decidable\_fraction}=0$ persistently),
the spread we introduce inside groups becomes the dominant source of
advantage variance and is not directionally aligned with the terminal
objective. This is consistent with
Open-Reasoner-Zero's~\cite{hu2025orz} finding that minimalist
rule-based rewards outperform hand-designed shaping in compute-
constrained settings.

% ============================================================
\section{Experiments}
\label{sec:exp}

\subsection{Setup}
Single-seed runs on a single A800 80GB. v1 trained for 76 steps before a
disk-full crash on checkpoint save (step 20 LoRA recovered, used as the
final model). v2-distill trained for 73 steps, terminating when training
\texttt{episode/success\_rate} collapsed from 0.91 (step 69) to 0.14 (step 73)
under the SFT pull. Evaluation uses $T=0.4$ matching training
\texttt{val\_kwargs}, single sample, multi-turn rollout in the same
environment as training.

\subsection{Main Results}

\begin{table}[t]
\centering
\caption{\textbf{Compile-pass rate (\%) on the three eval distributions.}
$n$ = number of prompts. Bold = best per column.
$\Delta$ = difference vs.\ v1.}
\label{tab:main}
\small
\setlength{\tabcolsep}{6pt}
\begin{tabular}{lrrrr}
\toprule
\textbf{Method} & \textbf{val} ($n{=}50$) & \textbf{test} ($n{=}50$) & \textbf{eval\_fixed} ($n{=}22$) & \textbf{weighted avg} \\
\midrule
Base (no RL)             & 70.0           & 74.0           & 40.9           & 61.6 \\
v1 (GiGPO + binary)      & \textbf{78.0}  & \textbf{76.0}  & \textbf{50.0}  & \textbf{68.0} \\
v2-distill (+ SFT $\alpha{=}0.1$) & 74.0           & 70.0           & 27.3           & 57.1 \\
\midrule
$\Delta_{\text{v1}-\text{base}}$ & $+8.0$ & $+2.0$ & $+9.1$ & $+6.4$ \\
$\Delta_{\text{v2}-\text{v1}}$   & $-4.0$ & $-6.0$ & $-22.7$ & $-10.9$ \\
\bottomrule
\end{tabular}
\end{table}

Three observations:
(1) RL training (v1) produces real generalization improvement on every
distribution, including the OOD \texttt{eval\_fixed} which uses a
modify/add/create task format the model never saw during training.
The $+9.1$pp gain on a task-format mismatch indicates the policy learned
something about producing valid Liquid templates rather than memorizing
the training prompt distribution.
(2) The Best-Trajectory SFT auxiliary loss \emph{hurts} on every distribution,
with the largest drop on OOD (\(-22.7\)pp). The in-loop validation curve
peaked higher than v1's, but on a fixed prefix that overlaps training
distribution; a clean re-evaluation reveals memorization.
(3) The $+65.6$pp lift from the single-example prompt
(\S\ref{sec:method}, $7.8 \to 73.4$\%) dwarfs the $+6.4$pp from RL.
Most of the absolute capability gain on this task is operating-regime,
not learning.

\subsection{Training Trajectories}
\label{sec:trajectories}

\begin{figure}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
  width=0.9\columnwidth, height=4.5cm,
  xlabel={Training step}, ylabel={val/success\_rate},
  xtick={0,10,20,30,40,50,60,70,80}, ytick={50,60,70,80,90},
  ymin=45, ymax=90, xmin=0, xmax=80,
  legend pos=south east,
  legend style={font=\scriptsize, inner sep=2pt, row sep=-1pt},
  tick label style={font=\small}, label style={font=\small},
  grid=major, grid style={dotted,gray!40},
  line width=1pt,
]
\addplot[color=darkblue, mark=*]
  coordinates {(0,73.4) (10,71.9) (20,78.1) (30,75.0)};
\addplot[color=darkred, mark=square, dashed]
  coordinates {(0,73.4) (10,79.7) (20,78.1) (30,67.2) (40,71.9)
               (50,76.6) (60,82.8) (70,48.4)};
\legend{v1 (binary), v2-distill (+SFT)}
\end{axis}
\end{tikzpicture}
\caption{\textbf{In-loop val trajectory ($n{=}32$ fixed prefix).} v1 (blue)
sustains 73--78\%; v2-distill (red) peaks at 82.8\% by step 60 then
collapses by step 70 as the SFT-on-winners pull memorizes the
training distribution. The training-success curve continued to rise
through step 69 ($0.91$) before collapsing to $0.14$ by step 73, a
classic ``train up, val down, then both crash'' signature.}
\label{fig:trajectory}
\end{figure}

% ============================================================
\section{Related Work}
\label{sec:related}

\textbf{Agentic RL vs.\ reasoning RL.} Recent open RL post-training
divides cleanly. \emph{Reasoning RL} (DeepSeek-R1~\cite{deepseek2025r1},
MiMo-7B~\cite{xiaomi2025mimo}, Open-Reasoner-Zero~\cite{hu2025orz})
trains single-turn solvers on verifiable math/code, with a 1.0 reward
gated by a checker (Math-Verify, test cases). \emph{Agentic RL}
(Cursor Composer 2~\cite{cursor2025composer2}, Kimi K2~\cite{kimi2025k2},
MiniMax-M1~\cite{minimax2025m1}, DeepSeek-V3.2~\cite{deepseek2025v32})
adds multi-turn tool use, environment-state changes, and---in the
Composer 2 case---auxiliary product penalties shaping
non-correctness behaviors. Our setting falls cleanly in the agentic
column: five tools (\texttt{list/describe/fix/submit}), 6-turn budget,
sparse terminal reward from the Sitemuse compiler. The negative
v3-shaped result (\S3.3) reports that the Composer 2 penalty recipe
does not naively transfer to our 4B-model / 64-episode-batch scale.

\textbf{Group-based agentic RL.} GiGPO~\cite{zeng2025gigpo} extends
GRPO~\cite{shao2024grpo} to multi-turn agents via anchor-state group
baselines. The mechanism assumes states recur across rollouts
(documented on ALFWorld and WebShop). On our task the state is a
JSON-parameterized Sitemuse validator response, which essentially
never recurs across rollouts; in practice the inner step-level group
collapses to size-1 clusters past step 2. HGPO~\cite{feng2026hgpo} and
SPEAR~\cite{spear2026} explore hierarchical groups and self-imitation
respectively. Our v1 uses GiGPO unmodified; we observe no reward
hacking under binary outcome reward in the primed regime, contrary to
predictions in the process-reward literature that motivate auxiliary
mechanisms.

\textbf{Process rewards in RL.} Math-Shepherd~\cite{wang2024mathshepherd}
introduces process reward models that score intermediate steps; PRMs
have since been shown vulnerable to Goodhart-style hacking when not
combined with sufficient capacity or RL constraints. Our analysis of
Compiler-OPD inherits this concern: the cap-K mechanism is a hand-tuned
patch, not a principled fix. Best-Trajectory
Distillation~\cite{lambert2025tulu3} avoids step shaping but, as our
v2-distill experiment shows, can over-pull toward training distribution
on small datasets.

\textbf{Verifiable RL on tool-using agents.} Concurrent work from
Ramp~\cite{ramp2026fastask} trains a 3B-active spreadsheet retrieval
model via GRPO with a similarly minimal reward
($1.0 \cdot \mathrm{correct} + 0.1 \cdot \mathrm{efficiency} + 0.05 \cdot \mathrm{concise}$),
no per-step shaping or auxiliary SFT, and beats Claude Opus 4.6 by 4pp.
Their setup uses a much larger effective batch (256 prompts $\times$ 8 rollouts
$=$ 2048 episodes per step vs.\ our 64), which we believe accounts for
their training stability without the auxiliary loss we
attempted in v2-distill.

% ============================================================
\section{Discussion and Limitations}
\label{sec:discussion}

\textbf{Single seed.} All numbers in Table~\ref{tab:main} are
single-seed point estimates; a $\pm 5$pp swing on $n{=}22$
\texttt{eval\_fixed} is plausible. Multi-seed runs are the obvious
next step before strong claims.

\textbf{Batch size.} Our 64 episodes/step is small. Concurrent
work~\cite{ramp2026fastask} uses 2048 with vanilla GRPO and reports
no instability; we suspect our v2-distill collapse at step 73 is partly
a small-batch effect (a few outlier groups dominating the SFT mask).
Scaling batch is the simplest next intervention.

\textbf{Async off-policy training.}
Off-policy training with importance-weighted clipping
(AIPO~\cite{ramp2026fastask}) decouples slow rollout generation
from policy updates and would be useful for our larger experiments.
We did not implement it; on a single A800 with $\sim$3-minute generation
and $\sim$2-minute updates per step, synchronous training was
adequate.

\textbf{Adversarial training data.} \texttt{train.jsonl} is generated by
a templated synthesizer with no decoy sections or ambiguous identifiers.
Adversarial workbook construction~\cite{ramp2026fastask} would
likely improve OOD robustness and is the most direct fix for
v2-distill's distribution-overfit failure mode.

\textbf{Dynamic sampling and Clip-Higher (deferred).} MiMo-7B's RL
recipe~\cite{xiaomi2025mimo} on the same verl framework we use applies
three modifications that should help our setting: (i)~DAPO
\emph{dynamic sampling}~\cite{yu2025dapo}, which over-samples and
filters out groups with passrate $\in \{0, 1\}$ so every group in the
batch contributes nonzero gradient; (ii)~\emph{Clip-Higher}, raising
the upper PPO clip bound to mitigate entropy collapse; and
(iii)~\emph{easy-data resampling} (10\% probability), which preserves
already-solved prompts in the rollout pool to stabilize late training.
In our run, $\mathrm{decidable\_fraction}=0$ persisted across all
40+ steps (batches were bimodal between all-pass and all-fail
groups), which is exactly the condition dynamic sampling resolves.
These three changes are one-line config edits in verl and are the
most direct next intervention to try; we did not include them in this
study to preserve the v1 / v2-distill / v3-shaped comparison's
otherwise-identical hyperparameter setting.

\textbf{Demonstration quality.} The few-shot example used to lift
base success from 7.8\% to 73.4\% (\S\ref{sec:method}) is itself a
minimal compile-pass shell with empty \texttt{settings} and
\texttt{blocks}. The agent learns to imitate this shape---a hack the
v3-shaped penalties were intended to suppress. Phi-4-reasoning's
strategy~\cite{phi4reasoning} of using a stronger teacher
(\emph{o3-mini}) to regenerate ``teachable'' demonstrations would
likely lift base further while making the empty-shell hack
non-optimal, simultaneously fixing v3-shaped's underlying motivation.

% ============================================================
\section{Conclusion}
\label{sec:conclusion}

For verifiable multi-turn coding agents, the question ``do we need
process rewards?'' has the same shape as the question ``do we need
reward shaping?'' in classical RL: the answer depends on whether the
sparse-reward regime is the actual operating regime or whether it is a
symptom of poor base policy. On a Shopify Horizon template-generation
task, a single in-context example moves a 4B base model from a
$7.8\%$ pass rate (sparse) to $73.4\%$ (healthy). In the healthy regime,
plain GiGPO with binary outcome reward improves all three test
distributions by $+2$ to $+9$pp. A more sophisticated auxiliary
Best-Trajectory SFT loss damages out-of-distribution generalization
by $-22.7$pp.

The lesson generalizes uneasily but it generalizes. Concurrent
work~\cite{ramp2026fastask} reaches the same conclusion on
spreadsheet retrieval: a minimal verifiable reward and an adequately
sized batch beats hand-designed process signal with frontier models
in the loop. We suspect this is the typical case rather than the
exception for verifiable code agent tasks, and that the energy
better spent on operating-regime engineering (priming, warm-starting,
adversarial data) than on per-step shaping.

% ============================================================
\bibliographystyle{plain}
\begin{thebibliography}{99}

\bibitem{le2022coderl}
Hung Le, Yue Wang, Akhilesh Deepak Gotmare, Silvio Savarese, and Steven C.H.\ Hoi.
\newblock CodeRL: Mastering Code Generation through Pretrained Models and Deep
  Reinforcement Learning.
\newblock In \emph{NeurIPS}, 2022.

\bibitem{zeng2025gigpo}
Xiangxiang Zeng, Feng Lang, et al.
\newblock GiGPO: Group-in-Group Policy Optimization for LLM Agent Training.
\newblock In \emph{NeurIPS}, 2025.
\newblock \url{https://github.com/langfengQ/verl-agent}

\bibitem{shao2024grpo}
Zhihong Shao, Peiyi Wang, Qihao Zhu, Runxin Xu, Junxiao Song,
  Mingchuan Zhang, Y.K.\ Li, Y.\ Wu, and Daya Guo.
\newblock DeepSeekMath: Pushing the Limits of Mathematical Reasoning in Open
  Language Models.
\newblock \emph{arXiv:2402.03300}, 2024.

\bibitem{wang2024mathshepherd}
Peiyi Wang, Lei Li, Zhihong Shao, R.X.\ Runxin Xu, Damai Dai,
  Yifei Li, Deli Chen, Yu Wu, and Zhifang Sui.
\newblock Math-Shepherd: Verify and Reinforce LLMs Step-by-step without Human
  Annotations.
\newblock In \emph{ACL}, 2024.

\bibitem{lambert2025tulu3}
Nathan Lambert et al.
\newblock T\"ulu 3: Pushing Frontiers in Open Language Model Post-Training.
\newblock \emph{arXiv:2411.15124}, 2025.
\newblock On-policy SFT / rejection-sampling SFT mixed with RL is a core recipe.

\bibitem{ramp2026fastask}
Ben Geist, Will Brown, and Ramp Labs.
\newblock Fast Ask: Post-training a small spreadsheet retrieval agent.
\newblock Ramp Labs blog post, May 2026.
\newblock \url{https://ramp.com/labs/fast-ask}

\bibitem{feng2026hgpo}
Shuo He, Lang Feng, Qi Wei, Xin Cheng, Lei Feng, and Bo An.
\newblock Hierarchy-of-Groups Policy Optimization for Long-Horizon Agentic Tasks.
\newblock In \emph{ICLR}, 2026.

\bibitem{spear2026}
Yulei Qin, Xiaoyu Tan, Zhengbao He, et al.
\newblock Learn the Ropes, Then Trust the Wins: Self-imitation with Progressive
  Exploration for Agentic Reinforcement Learning.
\newblock \emph{arXiv:2509.22601}, 2025.

\bibitem{qwen35}
Qwen Team.
\newblock Qwen3 Technical Report.
\newblock \emph{arXiv:2505.09388}, 2025.

\bibitem{jimenez2024swebench}
Carlos E.\ Jimenez, John Yang, Alexander Wettig, Shunyu Yao, Kexin Pei,
  Ofir Press, and Karthik Narasimhan.
\newblock SWE-bench: Can Language Models Resolve Real-World GitHub Issues?
\newblock In \emph{ICLR}, 2024.

\bibitem{cursor2025composer2}
Cursor Research Team.
\newblock Composer 2 Technical Report.
\newblock 2025.
\newblock \url{https://cursor.com/resources/Composer2.pdf}

\bibitem{kimi2025k2}
Kimi Team.
\newblock Kimi K2: Open Agentic Intelligence.
\newblock \emph{arXiv:2507.20534}, 2025.

\bibitem{minimax2025m1}
MiniMax-AI.
\newblock MiniMax-M1: Scaling Test-Time Compute Efficiently with Lightning
  Attention.
\newblock \emph{arXiv:2506.13585}, 2025.

\bibitem{deepseek2025v32}
DeepSeek-AI.
\newblock DeepSeek-V3.2: Pushing the Frontier of Open Large Language Models.
\newblock \emph{arXiv:2512.02556}, 2025.

\bibitem{deepseek2025r1}
DeepSeek-AI.
\newblock DeepSeek-R1: Incentivizing Reasoning Capability in LLMs via
  Reinforcement Learning.
\newblock \emph{arXiv:2501.12948}, 2025.

\bibitem{xiaomi2025mimo}
Xiaomi LLM-Core Team.
\newblock MiMo: Unlocking the Reasoning Potential of Language
  Model---From Pretraining to Posttraining.
\newblock \emph{arXiv:2505.07608}, 2025.

\bibitem{hu2025orz}
Jingcheng Hu et al.
\newblock Open-Reasoner-Zero: An Open Source Approach to Scaling Up RL on
  the Base Model.
\newblock \emph{arXiv:2503.24290}, 2025.

\bibitem{yu2025dapo}
Qiying Yu et al.
\newblock DAPO: An Open-Source LLM Reinforcement Learning System at Scale.
\newblock \emph{arXiv:2503.14476}, 2025.

\bibitem{phi4reasoning}
Microsoft.
\newblock Phi-4-reasoning Technical Report.
\newblock \emph{arXiv:2504.21318}, 2025.

\end{thebibliography}

% ============================================================
\appendix
\section{In-loop val vs.\ Held-out re-evaluation: A Cautionary Sample}
\label{app:val_disagreement}

The in-loop \texttt{val/success\_rate} computed during training (on a
deterministic 32-prompt prefix of \texttt{val.jsonl}) and the post-hoc
re-evaluation on the full $n=50$ \texttt{val.jsonl} disagree by
nontrivial margins for v2-distill:

\begin{center}
\small
\begin{tabular}{lrr}
\toprule
\textbf{Checkpoint} & \textbf{In-loop val} ($n{=}32$) & \textbf{Post-hoc val} ($n{=}50$) \\
\midrule
v1 step\_20         & 78.1 & 78.0 \\
v2-distill step\_60 & 82.8 & 74.0 \\
\bottomrule
\end{tabular}
\end{center}

The in-loop number for v2-distill at step 60 was the run's apparent peak
and would have been a misleading basis for ``best LoRA'' selection; the
held-out re-evaluation reverses the ordering. We attribute this to
training-distribution overlap with the fixed val prefix combined with
SFT-on-winners memorization. Practically, post-hoc evaluation on a
larger and ideally OOD set is required before declaring a checkpoint
``best.''

\end{document}
